---
title: "p8105_hw5_jc6422"
author: "Jianing Chen"
date: "2024-11-05"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
```

## Question 1

Write a function

```{r}
shared_birthday = function(n) {
  birthdays = sample(1:365, n, replace = TRUE)
  return(any(duplicated(birthdays)))
}
```

Run this function 10000 times for each group size between 2 and 50.

```{r}
group_sizes = 2:50
simulations = 10000

results = 
  tibble(group_size = group_sizes) %>%
  mutate(
    output_lists = map(group_size, ~rerun(simulations, shared_birthday(.x))),
    estimate_df = map(output_lists, ~tibble(shared_birthday = unlist(.)))
     )%>%
  select(-output_lists) %>%
  unnest(estimate_df) %>%
  group_by(group_size) %>%
  summarize(probability = mean(shared_birthday), .groups = 'drop')

results
```

Make a plot showing the probability as a function of group size.

```{r}
results %>%
  ggplot(aes(x = group_size, y = probability)) +
  geom_line() +
  geom_point() +
  labs(title = "Probability of Shared Birthday vs Group Size",
       x = "Group Size",
       y = "Probability of Shared Birthday") +
  theme_minimal()
```

This plot shows the relationship between the probability of shared birthday and group size, as the group size increases, the probability of at least two people sharing a birthday rises rapidly. This growth is nonlinear. The probability increasing quickly at first and flattening as it approaches 1 according to the group size approaches to 50.

## Question 2

Define a function to obtain the estimate and p-value

```{r}
n = 30         
sigma = 5  
times = 5000 
get_estimate_pvalue = function(mu) {
  estimate = numeric(times)
  pvalue = numeric(times)
  for(i in 1:times) {
    x = rnorm(n, mu, sigma)
    t_test_result = broom::tidy(t.test(x, mu = 0, alternative = "two.sided"))
    estimate[i] = as.numeric(t_test_result$estimate)
    pvalue[i] = as.numeric(t_test_result$p.value)
  }
  result = data.frame(
    mu = rep(mu, times),
    estimate = estimate,
    pvalue = pvalue
  )
  return(result)
}

# get the estimate and p-value with different mu
result = get_estimate_pvalue(mu = 0)
for(i in 1:6){
  result = rbind(result, get_estimate_pvalue(mu = i))
}


```

Calculate the proportion of times the null was rejected. 

```{r}
df1 = result %>%
  group_by(mu) %>%
  summarise(proportion = mean(pvalue < 0.05))
```

Make a plot showing the relationship between effect size and power of the test.

```{r}
ggplot(df1, aes(x = mu, y = proportion)) +
  geom_point() +
  geom_line() +
  labs(x = "True Mean (mu)", y = "Power") +
  ggtitle("Power vs Effect Size") +
  theme_minimal()
```

From this figure, we can observe that the larger the effect size, the higher the power.

Calculate the average estimate of mu

```{r}
df2 = result %>%
  group_by(mu) %>%
  summarise(estimate = mean(estimate))
```

Make a plot showing the average estimate of mu and true mu

```{r}
ggplot(df2, aes(x = mu, y = estimate)) +
  geom_point() +
  geom_line() +
  labs(x = "True Mean (mu)", y = "Average Estimate of mu") +
  ggtitle("Average Estimated mu vs True mu") +
  theme_minimal()
```
Calculate the average estimate of mu only in samples for which the null was rejected.

```{r}
df3 = result %>%
  filter(pvalue < 0.05) %>%
  group_by(mu) %>%
  summarise(estimate = mean(estimate))
```

Make a plot overlay on the first plot

```{r}
df = rbind(df2, df3)
df$group = c(rep("Average Estimate of mu", 7), rep("Average Estimate of mu (mu reject H0)", 7))

ggplot(df, aes(x = mu, y = estimate, color = group, group = group)) +
  geom_point() +
  geom_line() +
  labs(x = "True Mean (mu)", y = "Average Estimate of mu") +
  ggtitle("Average Estimated mu vs True mu") +
  theme_minimal()
```

From this figure, we can see that the the sample average of mu across tests for which the null is rejected approximately is not equal to the true value of mu. Because only those samples with large effects are more likely to be rejected, the average of these samples with large effects will be larger than the true value.

## Question 3

Load the data

```{r}
data = read_csv("homicide-data.csv")
```

In this dataset, there are `r data %>% distinct(city) %>% nrow()` unique cities. There are `r nrow(data)`observations. There are `r ncol(data)` variables. The variables are `r names(data)`


Create a `city_state` variable and then summarize within cities.

```{r}
summary = data %>%
  mutate(city_state = str_c(city, ", ", state)) %>%
  group_by(city_state) %>%
  summarize(
    total_homicides = n(),
    unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
  )
summary
```

For the city of Baltimore, MD, use ` pop.test` function to estimate the proportion of homicides that are unsolved.

```{r}
baltimore_data = summary %>% 
  filter(city_state == "Baltimore, MD") 
  
baltimore_test = prop.test(baltimore_data$unsolved_homicides, baltimore_data$total_homicides)
baltimore_test
```

Apply `broom::tidy` to this project and pull the estimated proportion and confidence intervals.

```{r}
baltimore_result = broom::tidy(baltimore_test)

estimate_prop = baltimore_result$estimate
estimate_prop
```

```{r}
conf_low = baltimore_result$conf.low
conf_low
```

```{r}
conf_high = baltimore_result$conf.high
conf_high
```

Based on the result, the estimate proportion is 0.646, and the 95% CI is [0.628, 0.663]

Run `prop.test` for each of the cities in the dataset, and create a tidy dataframe with estimated proportions and CIs for each city.

```{r}
city = summary %>%
  mutate(
    test_result = purrr::map2(unsolved_homicides, total_homicides, ~ prop.test(.x, .y)),
    tidy_result = purrr::map(test_result, broom::tidy)
  ) %>%
  unnest(tidy_result) %>%
  select(city_state, estimate, conf.low, conf.high)

city
```

Create a plot that shows the estimates and CIs for each city.

```{r,fig.height=10, fig.width= 7}
ggplot(city, aes(x = reorder(city_state,estimate), y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.3) +
  coord_flip() +
  labs(
    title = "Proportion of Unsolved Homicides by City",
    x = "City",
    y = "Estimated Proportion of Unsolved Homicides"
  ) +
  theme_minimal()
```

This plot shows the proportion of unsolved homicides for various U.S. cities. Chicago, IL, have the highest proportions of unsolved homicides, with estimates close to 0.75. Tulsa, AL, have the lowest unsolved homicide rates, with estimates close to 0. Error bars show the 95% confidence interval for each estimate. Chicago, IL tend to have narrower intervals, suggesting that these estimates are reliable. Tulsa, AL, has a wider confidence interval, which suggests a greater uncertainty.

