---
title: "p8105_hw5_jc6422"
author: "Jianing Chen"
date: "2024-11-05"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Question 1

Write a function

```{r}
shared_birthday = function(n) {
  birthdays = sample(1:365, n, replace = TRUE)
  return(any(duplicated(birthdays)))
}
```

Run this function 10000 times for each group size between 2 and 50.

```{r}
group_sizes = 2:50
simulations = 10000

results = 
  tibble(group_size = group_sizes) %>%
  mutate(
    output_lists = map(group_size, ~rerun(simulations, shared_birthday(.x))),
    estimate_df = map(output_lists, ~tibble(shared_birthday = unlist(.)))
     )%>%
  select(-output_lists) %>%
  unnest(estimate_df) %>%
  group_by(group_size) %>%
  summarize(probability = mean(shared_birthday), .groups = 'drop')

results
```

Make a plot showing the probability as a function of group size.

```{r}
results %>%
  ggplot(aes(x = group_size, y = probability)) +
  geom_line() +
  geom_point() +
  labs(title = "Probability of Shared Birthday vs Group Size",
       x = "Group Size",
       y = "Probability of Shared Birthday") +
  theme_minimal()
```

This plot shows the relationship between the probability of shared birthday and group size, as the group size increases, the probability of at least two people sharing a birthday rises rapidly. This growth is nonlinear. The probability increasing quickly at first and flattening as it appraches 1 according to the group size appraches to 50.
